DeconvOptim.jl - Signal Deconvolution with Julia

### 2021-09-15 paper/header.tex
Update latex header [no ci]

\hypersetup{
pdftitle = {DeconvOptim.jl - Image Deconvolution with Julia},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Felix Wechsler, Rainer Heintzmann},
pdfkeywords = {Julia, Image Processing, Deconvolution, Microscopy},
}

>>>>

\hypersetup{
pdftitle = {DeconvOptim.jl - Signal Deconvolution with Julia},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Felix Wechsler, Rainer Heintzmann},
pdfkeywords = {Julia, Image Processing, Deconvolution, Microscopy},
}
